---
title: "Covid"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Lusungu Mkandawire^[__Contributions:__  \newline _The authors would like
  to thank no institution for money donated to this project. Thank you sincerely._]
Ref1: Stellenbosch University, South Africa
Email1: lsmkandawire\@gmail.com
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: null
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Purpose
The purpose of this project  is to produce some statistics and figures on the evolution of the Covid outbreak. The statistics and figures will aid in writing Covid reports in the New York Times. The data used has been provided by Our World in Data (OWID) 


```{r}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(lubridate)




# Data loading:

library(readr)
covid_data_description <- read_csv("data/Covid/covid_data_description.csv")
Deaths_by_cause <- read_csv("data/Covid/Deaths_by_cause.csv")
data <- read_csv("data/Covid/owid-covid-data.csv")
```
```{r}
# loading functions
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

#The first thing done is showing how African countries’ experience has differed from other regions.

```{r}
g  <- casesovertime (data)
g

```

```{r}
gg <- newcasesovertime (data)

gg
```
As the graphs can show Africa did not have high levels of total Covid cases neither of new casescompared to other regions.

```{r}
deathsdiseases(Deaths_by_cause, owid_covid_data)
```

According to death caused by different diseases
